Ideal model selection is impossible

### 2014-10-23 Facticity/Facticity/paper.tex
nog iets preciezer over die prefix functie

\begin{lemma}
  For sufficiently large $c$ the set $B^n$ is nonempty for all $n$.
\end{lemma}

@@

\begin{lemma}[I think this is it]
Let $\psi_1,\psi_2,\ldots$ be any acceptable numbering.
For every $c$ there is another acceptable numbering $\phi_1,\phi_2,\ldots$ such that for all partial recursive functions $f$ we have
\[
K^\phi(f)-K^\psi(f) \ge c.
\]
\end{lemma}
\begin{proof}
Define $\tau$ by $\psi_\tau(\bar k p) = j$ where $j$ is given by $1^r 0 j = \psi_k(p)$. In other words, it is a universal element for $\psi$ that subsequently strips the prefix $1^r 0 $ from the output; this operation is clearly still partial recursive. Also note that this function has a fixed index -- it does not have to know $r$. For completeness define $\psi_\tau$ to infinity if the output is not in the correct format.

Now define a new acceptable numbering $\phi_1,\phi_2,\ldots$ as follows:
\[
\phi_{1^r0 j}(p)=\psi_j(p)
\]
For any given partial recursive function $f$, we now compare $K^\phi(f)$ and $K^\psi(f)$.
For $\phi$ it is:
\[
K^\phi(f) = \min\{K^\phi(i):\phi_i = f\}.
\]
Let $i^-$ be the index that achieves the minimum, and let $i^*$ be the shortest $\phi$-program that computes it, that is, $i^*=\bar a b$ such that $\phi_a(b)=i^-$.
Then the codelength is $K^\phi(f)=K^\phi(i^-)=|i^*|$. Moreover, we must have $a=1^r0 k$ where $k$ is the index of the corresponding function in the $\psi$-enumeration: $\psi_k(b)=i^-$.

To find an index of $f$ in the $\psi$-enumeration, note that $f=\phi_{i^-}=\phi_{1^r 0 j^-} = \psi_{j^-}$. We have $K^\psi(f) \le K^\psi(j^-)$; we proceed to provide a small $\psi$-program for $j^-$. This can be done because we have set things up so that $\psi_\tau(\bar k b)=j^-$. Thus, the $\psi$-program is $j^*=\bar\tau\bar k b$. The difference in length is
%
\[
|i^*|-|j^*| = |\bar a b|-|\bar\tau\bar k b| = |\overline{1^r 0 k}| - |\bar\tau| - |\bar k| \approx r-|\bar\tau|.
\]
%
(Here the $\approx$ is used because the prefix function has a slightly different effect on the two terms; however this is an unimportant detail that can be ironed out later).

Thus, by choosing $r>|\bar\tau|+c$ we can guarantee that $K^\phi$ sucks by at least $c$ bits. Yay!
\end{proof}

\begin{proof}[Proof (combined)]
First note that there is a $c'$ such that 
\begin{equation}
	K(1^r 0  x) + c' \geq K(x) \label{eq:prelim1}
\end{equation}
for all $x$, since we can create a program that first runs the shortest program for $1^r 0 x$ and then strips the prefix $1^r 0$ from the result.

Define $\phi_{1^r0i}(x) = \psi_{i}(x)$, with $\phi_{j}(x) = \infty$ if $j$ does not contain a zero. Intuitively, any $\phi$-program is $r+1$ bits longer than the corresponding $\psi$-program. However, the used prefix function complicates this slightly. [TODO assume the prefix function to be convex.] But all we need is the bound
\begin{equation}\label{eq:prelim2}\begin{split}
K^\phi(x) &= \min \{ |\overline{1^r 0 \imath}| y : \phi_{1^r 0 i}(y) = x \}\\
&  \ge \min\{|1^r0\bar\imath y| : \phi_{1^r 0 i}(y) = x \}\qquad\tn{(using convexity of $\bar\cdot$)}\\
& = r+1 +\min\{|\bar\imath y| : \psi_i(y) = x \}\\
& = r+1+K^\psi(x).
\end{split}\end{equation}

>>>>

\begin{lemma}
  For sufficiently large $c$ the sets $B^n$ are nonempty for all $n$.
\end{lemma}

@@

\begin{lemma}
Assume the prefix function $\bar\cdot$ used in the definition of complexity is such that $\bar x-x$ is monotonically increasing. Let $\psi_1,\psi_2,\ldots$ be any acceptable numbering. Then for every $c$ there is another acceptable numbering $\phi_1,\phi_2,\ldots$ such that for all partial recursive functions $f$ we have
\[
K^\phi(f)-K^\psi(f) \ge c.
\]
\end{lemma}
\begin{proof}
First note that there is a $c'$ such that 
\begin{equation}
	K(1^r 0  x) + c' \geq K(x) \label{eq:prelim1}
\end{equation}
for all $x$, since we can create a program that first runs the shortest program for $1^r 0 x$ and then strips the prefix $1^r 0$ from the result.

Define $\phi_{1^r0i}(x) = \psi_{i}(x)$, with $\phi_{j}(x) = \infty$ if $j$ does not contain a zero. Intuitively, any $\phi$-program is $r+1$ bits longer than the corresponding $\psi$-program. However, the used prefix function complicates this slightly. But all we need is the bound
\begin{equation}\label{eq:prelim2}\begin{split}
K^\phi(x) &= \min \{ |\overline{1^r 0 \imath}| y : \phi_{1^r 0 i}(y) = x \}\\
&  \ge \min\{|1^r0\bar\imath y| : \phi_{1^r 0 i}(y) = x \}\qquad\tn{(using assumption on $\bar\cdot$)}\\
& = r+1 +\min\{|\bar\imath y| : \psi_i(y) = x \}\\
& = r+1+K^\psi(x).
\end{split}\end{equation}
